---
title: "Worksheet 4"
author: "LG Grace C. Sabio"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\hfill\break
1. The table below shows the data about shoe size and height. Create a data frame..
```{r, vector = TRUE}
shoe_size <- data.frame (
       shoeSize = c(6.5, 9.0, 8.5, 8.5, 10.5, 7.0, 9.5, 9.0, 13.0, 7.5, 
                    10.5, 8.5, 12.0, 10.5, 13.0, 11.5,8.5, 5.0, 10.0,
                    6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0 ),
       height = c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0,
                  64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0,
                  72.0, 66.0, 64.0, 67.0,73.0, 69.0, 72.0, 70.0, 69.0, 70.0),
       Gender = c('F', 'F', 'F', 'F', 'M', 'F', 'F', 'F', 'M', 'F', 'M', 'F', 'M', 'M', 
                  'M', 'M', 'F', 'F', 'M', 'F', 'F', 'M','M', 'F', 'M', 'M', 'M', 'M')
       
)
shoe_size

names(shoe_size) <- list("Shoe size", "Height", "Gender") 
shoe_size
```
a. Describe the data
```{r, vector = TRUE}
# The table shows three columns such as "Shoe size", "Height", and "Gender". 
#I noticed that the taller the person is, the bigger the shoe size is. 
#Mostly males had bigger shoe size and taller compare to females.
```
b. Find the mean of shoe size and height of the respondents.
```{r, vector = TRUE}
sizeNheight <- subset(shoe_size[ 1:2])
sizeNheight
meanSH <- colMeans(sizeNheight)
meanSH
```
c. Is there a relationship between shoe size and height? Why?
```{r, vector = TRUE}
sizeNheight <- subset(shoe_size[c( 1, 2)])
meanSH <- colMeans(sizeNheight)
mean(meanSH)
 # Yes. because I think the taller a person is, the bigger the shoe size he has.

```
\hfill\break
2. Construct character vector months to a factor with factor() and assign the result to
factor_months_vector. Print out factor_months_vector and assert that R prints out
the factor levels below the actual values.
```{r, vector = TRUE}
months_vector <- c("March","April","January","November","January","September",
                   "October","September","November","August","January","November",
                  "November","February","May","August","July","December","August",
                  "August","September","November","February","April")
factor_months_vector <- factor(months_vector)
factor_months_vector
```
\hfill\break
3. Then check the summary() of the months_vector and factor_months_vector. |
```{r, vector = TRUE}
summary_months <- summary(months_vector)
summary_months

```
```{r, vector = TRUE}
summary_factor_months <- summary(factor_months_vector)
summary_factor_months

#
```
Interpret the results of both vectors. Are they both equally useful in this case?
```{r, vector = TRUE}
# The summary() of the months_vector displays the length, class, and mode of the vector
#months_vector while the summary() of the factor_months_vector displays the different months 
#of the year and their corresponding frequency or how many times it was mentioned in the vector.
# They are both equally useful in this case.
```

\hfill\break
4. Create a vector and factor for the table below.
```{r, vector = TRUE}
factor_data <- c("East", "West", "North")
factor_data
new_order_data <- factor(factor_data,levels = c("East","West","North"))
print(new_order_data)

```
\hfill\break
5. Enter the data below in Excel with file name = import_march.csv
a. Import the excel file into the Environment Pane using read.table() function.Write the code.
```{r, vector = TRUE}
Import <- read.table("import_march.csv", header =  TRUE, sep = ",")
Import
```
b. View the dataset. Write the code and its result.
```{r, vector = TRUE}
# View(import_march_csv)

```