---
title: "Worksheet 6"
author: "LG Grace C. Sabio"
date: "`r Sys.Date()`"
output: pdf_document
---
```{r, vector = TRUE}
library(dplyr)
library(ggplot2)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\hfill\break
1. How many columns are in mpg data set? How about the number of rows? Show the codes and its result.
```{r, vector = TRUE}
data(mpg)
mpg_data <- glimpse(mpg)
mpg_data 
#There are 11 columns, and 234 rows in mpg data set.
```
\hfill\break

2. Which manufacturer has the most models in this data set? 
```{r, vector = TRUE}
mostModels <- mpg_data %>% group_by(manufacturer) %>% count()
mostModels
colnames(mostModels) <- c("Manufacturer","Counts")
mostModels
#  Dodge, it has 37 models.
```
Which model has the most variations?
```{r, vector = TRUE}
mostVar<- mpg_data %>% group_by(model) %>% count()
mostVar
colnames(mostVar) <- c("Model","Counts")
mostVar
# Caravan 2wd model, it has 11 variations.
```
a. Group the manufacturers and find the unique models. Copy the codes and result.
```{r, vector = TRUE}
manUnique <- mpg_data %>% group_by(manufacturer, model) %>% distinct() %>% count()
manUnique
colnames(manUnique) <- c("Manufacturer", "Model","Counts")
manUnique
```
b. Graph the result by using plot() and ggplot(). Write the codes and its result.
```{r, vector = TRUE}
plot(manUnique)

```

```{r, vector = TRUE}
ggplot(manUnique, aes(x = Manufacturer, y = Model)) + geom_point()
```
\hfill\break

3. Same dataset will be used. You are going to show the relationship of the model 
and the manufacturer.

```{r, vector = TRUE}
ggplot(manUnique, aes(x = Model, y = Manufacturer )) + geom_point(color='blue')
```

a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
```{r, vector = TRUE}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
# It displays black points.The manufacturers can be read easily while the models cannot be. 
```
b. For you, is it useful? If not, how could you modify the data to make it more informative?
```{r, vector = TRUE}
# The data is organized but the model names on x-axis are not readable enough.
# Maybe by modifying or adjusting its angle will make it more informative.

```
\hfill\break
4. Using the pipe (%>%), group the model and get the number of cars per model.
 Show codes and its result.
```{r, vector = TRUE}
carsModel <- mpg_data %>% group_by(model) %>% count()
carsModel
colnames(carsModel) <- c("Model","Counts")
carsModel

```
a. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result.
```{r, vector = TRUE}
barg <- ggplot(carsModel, aes( x = Model, y = Counts, fill = Model)) + 
  labs(title = "Numbers of cars per Model", y = "Number of Cars", x = "Model")  +
  geom_bar(stat = "identity") + theme(legend.position = "none")

barg +
coord_flip()
           
```
 b. Use only the top 20 observations. Show code and results.
```{r, vector = TRUE}
head(carsModel, n = 20)
```
\hfill\break
5. Plot the relationship between cyl - number of cylinders and displ - engine displacement 
using geom_point with aesthetic colour = engine displacement. Title should be 
“Relationship between No. of Cylinders and Engine Displacement”.
a. Show the codes and its result.
```{r, vector = TRUE}
ggplot(mpg, mapping = aes(x = displ , y = cyl)) + labs(title = "Relationship between No. 
     of Cylinders and Engine Displacement") + geom_point(aes(color = "engine displacement"))

```
b. How would you describe its relationship?

```{r, vector = TRUE}
# I would describe their relationship as consistent or stable
```
\hfill\break
6. Get the total number of observations for drv - type of drive train (f = front-wheel drive, 
r = rear wheel drive, 4 = 4wd) and class - type of class (Example: suv, 2seater, etc.).
```{r, vector = TRUE}

front <- subset(mpg, drv == 'f')
front <- nrow(front)

rear <- subset(mpg, drv == 'r')
nrow(rear)


four <- subset(mpg, drv == '4')
nrow(four)

suv <- subset(mpg, class == 'suv')
nrow(suv)


compact <- subset(mpg, class == 'compact')
nrow(compact)


midsize <- subset(mpg, class == 'midsize')
nrow(midsize)


twoseater <- subset(mpg, class == '2seater')
nrow(twoseater)


minivan <- subset(mpg, class == 'minivan')
nrow(minivan)


pickup <- subset(mpg, class == 'pickup')
nrow(pickup)

sub <- subset(mpg, class == 'subcompact')
nrow(sub)

```
Plot using the geom_tile() where the number of observations for class be used as a fill for aesthetics.
a. Show the codes and its result for the narrative in #6.
```{r, vector = TRUE}
ggplot(mpg, aes(drv, class)) +
  geom_tile (aes(fill = class))
```
b. Interpret the result.
```{r, vector = TRUE}
# The result shows that if there is a relationship between a class and drv, a tile was created.
```
\hfill\break
7. Discuss the difference between these codes. Its outputs for each are shown below.
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```{r, vector = TRUE}
# In the first code, the "colour = blue" code was inside the function aes(), so it failed 
# to give a color blue dots or points. on the other hand, the second code was executed and 
# was in its proper place or outside the aes() function,and in result the plot was shown accordingly.
```
\hfill\break
8. Try to run the command ?mpg. What is the result of this command?
```{r, vector = TRUE}
?mpg
# The result was shown on the Files pane specifically in the Help Tab that contains its description, usage,and format.
```
a. Which variables from mpg data set are categorical?
- Categorical variables in mpg include: manufacturer, model, trans (type of transmission), 
drv (front-wheel drive, rear-wheel, 4wd), fi (fuel type), and class (type of car)

b. Which are continuous variables?
- Continuous variables in mpg include: displ (engine displacement in litres), cyl 
 (number of cylinders), cty (city miles/gallon), and hwy (highway gallons/mile)

c. Plot the relationship between displ (engine displacement) and hwy(highway miles
 per gallon). Mapped it with a continuous variable you have identified in 
5-b. What is its result? Why it produced such output?
```{r, vector = TRUE}
ggplot( data = mpg) +
   geom_point(mapping = aes(x = displ , y = hwy, col = displ)) 
```

  
```{r, vector = TRUE}
# It produced such output because we plot the relationship between the displ and hwy and its geom_point color should be mapped in with a continuous variable.
```
\hfill\break
9. Plot the relationship between displ (engine displacement) and hwy(highway miles
 per gallon) using geom_point(). Add a trend line over the existing plot using
  geom_smooth() with se = FALSE. Default method is “loess”.
```{r, vector = TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=displ)) +
  geom_smooth(se =FALSE)
```
\hfill\break
10. Using the relationship of displ and hwy, add a trend line over existing plot. Set the
se = FALSE to remove the confidence interval and method = lm to check for linear modeling.
```{r, vector = TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=displ)) +
  geom_smooth(se =FALSE,method = lm)
```

